Experience Report:

### 2010-03-16 doc/icfp-2010/main.tex
more fault tolerance on fault tolerance

@@

>>>>

The main issue in any distributed computing environment is ability to
handle faults, which is also a distinguishing feature of our library.
Faults are mainly of two kinds: either a worker is stopped, and
possibly later restarted; or a worker is temporarily or permanently
unreachable on the network. To provide fault tolerance, our master
implementation is keeping track of the status of each worker. 
This status is controlled by two timeout parameters $T_1$ and $T_2$
and \of{Ping} and \of{Pong} messages sent by master and workers,
respectively. There are four possible statuses for a worker: 
\begin{description}
\item[\of{not connected}:] the worker is still to be
  connected to perform any useful task;
\item[\of{alive}:] the worker has sent some message recently,
  within $T_1$ seconds;
\item[\of{pinged}:] the worker has not sent any message recently (for more
  than $T_1$ seconds) and the master hash sent it a \of{Ping} message
  within the last $T_2$ seconds;
\item[\of{unreachable}:] the worker has not yet responded to the \of{Ping}
  message (for more than $T_2$ seconds).
\end{description}
% TODO picture
Whenever we receive a message from a worker, its status changes to
\of{alive} and its timeout value is reset.

Fault tolerance is achieved by exploiting the statues of workers as
follows. First, tasks are only assigned to workers with either
\of{alive} or \of{pinged} status. Second, whenever a worker executing
a task $t$ moves to status \of{not connected} or \of{unreachable}, the
task $t$ is rescheduled, which means

@@

speeding up the end of computation with duplicate tasks on idle workers
(straightforward since already done for fault tolerance)
